Deconstructing Simple and Choice Decision and Movement Time Across the Spectrum of Schizophrenia Genetic Risk

### 2022-12-20 README.Rmd
added a few details to main files

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Deconstructing Simple and Choice Decision and Movement Time Across the Spectrum of Schizophrenia Genetic Risk"
```

@@

> Authors, (YYYY).
> *`r Title`*.
> Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (YYYY).
> *`r Title`*.
> Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`.
> Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`).
> *Compendium of R code and data for `r Title`*.
> Accessed `r format(Sys.Date(), "%d %b %Y")`.
> Online at <https://doi.org/xxx/xxx>

@@

-   [:file_folder: paper](/analysis/paper): R Markdown source document for manuscript. Includes code to reproduce the figures and tables generated by the analysis. It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)
-   [:file_folder: data](/analysis/data): Data used in the analysis.
-   [:file_folder: figures](/analysis/figures): Plots and other illustrations
-   [:file_folder: supplementary-materials](/analysis/supplementary-materials): Supplementary materials including notes and other documents prepared and collected during the analysis.

### 2022-12-20 analysis/paper/paper.qmd
added a few details to main files

---
title: "Title Goes Here"
author:
  - Jane Doe:
      correspondence: "yes"
      email: janedoe@fosg.org
      orcid: 0000-0003-1689-0557
      institute:
        - fosg
        - fop
  - John Q. Doe:
      institute: fosg
      orcid: 0000-0003-1689-0558
  - Peder Ås:
      institute: fosg
      orcid: 0000-0003-1689-0559
  - Juan Pérez:
      orcid: 0000-0003-1689-0551
      institute:
        - name: Acme Corporation
  - Max Mustermann:
      orcid: 0000-0003-1689-0552
institute:
  - fosg:
      name: Formatting Open Science Group
      address: 23 Science Street, Eureka, Mississippi, USA
  - fop: Federation of Planets
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

>>>>

---
title: "Deconstructing Simple and Choice Decision and Movement Time Across the Spectrum of Schizophrenia Genetic Risk"
author:
  - Joey Trampush:
      correspondence: "yes"
      email: joey.trampush@med.usc.edu
      orcid: 0000-0003-0830-508X
      institute:
        - usc
        - fop
  - John Q. Doe:
      institute: fosg
      orcid: 0000-0003-1689-0558
  - Dwight Dickinson:
      institute: nimh
      orcid: 0000-0003-1689-0559
  - Juan Pérez:
      orcid: 0000-0003-1689-0551
      institute:
        - name: Acme Corporation
  - Max Mustermann:
      orcid: 0000-0003-1689-0552
institute:
  - fosg:
      name: Keck School of Medicine of USC
      address: 23 Science Street, Eureka, Mississippi, USA
  - fop: Federation of Planets
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---
